A Study of an X-Ray Vision Tracking Task in Simulated Augmented Reality

### 2009-06-25 Paper/paper.tex
Added descriptions of why we chose the thresholds

\title{A Study of Target Following with X-Ray Vision in 
%Simulated
Augmented Reality}

@@

\author{
Submission 165
%Roy G. Biv\thanks{e-mail: roy.g.biv@aol.com}\\ Starbucks Research %
%\and Ed Grimley\thanks{e-mail:ed.grimley@aol.com}\\Nigel Mansell\thanks{nigelf1@msn.com}\\ Grimley Widgets, Inc. %
%\and Martha Stewart\thanks{e-mail:martha.stewart@marthastewart.com}\\ Martha Stewart Enterprises \\ Microsoft Research
}

@@

We can more explicitly detect the participant's state by applying a threshold $\tau$ to the data.  The threshold specifies the maximum angular error that still represents successful following of the target. 
%When the error rises above the threshold, we consider the participant lost.
We use a threshold of one quarter of the total horizontal field of view of the HMD, $\tau = 12$ degrees.
% TODO: how to motivate this threshold?
\begin{figure}[t]
	\centering
	\includegraphics[width=3.5in]{figures/tt_deadlen.pdf}
	\caption{\label{fig:tt_deadlen}Box plot of the amount of time the target is near the crosshairs versus the length of sensor dropouts.}
\end{figure}
Using this threshold we measure a participant's ``time to failure,'' the time until the a lost state is encountered.  However, this may not be a very descriptive measure, since a participant may reach the lost state sooner or later depending on the movement of the avatars, which varies between trials.

We also consider a measurement we call ``Time Following Target,'' which is the amount of time spent in the target following state.  This metric seems to most generally represent how well a participant performed.  Trials with either more or longer lost periods will result in a lower total time following the target.

For a more specific measure of performance, we count the number of times a participant reaches the lost state in a trial.  We only record a lost state when the error stays above the threshold $\tau$ for a minimum of 0.5 seconds.
% TODO: how to motivate this threshold?

>>>>

\title{A Study of an X-Ray Vision Tracking Task in Simulated Augmented Reality}

@@

\author{
Submission 191
%Roy G. Biv\thanks{e-mail: roy.g.biv@aol.com}\\ Starbucks Research %
%\and Ed Grimley\thanks{e-mail:ed.grimley@aol.com}\\Nigel Mansell\thanks{nigelf1@msn.com}\\ Grimley Widgets, Inc. %
%\and Martha Stewart\thanks{e-mail:martha.stewart@marthastewart.com}\\ Martha Stewart Enterprises \\ Microsoft Research
}

@@

We can more explicitly detect the participant's state by applying a threshold $\tau$ to the data.  The threshold specifies the maximum angular error that still represents successful following of the target. 
%When the error rises above the threshold, we consider the participant lost.
While conducting the trials we noticed that the participants spent a majority of the time correctly following Top Hat, computing the median angular error at each time-step across all trials gave us values mostly around 4 degrees so we consider values close to this as successful tracking.  We also noticed that during trials as Top Hat would change direction the participant's angular error would increase a small amount for a short time, without losing the target.  As a result we doubled the 4 degrees, giving us a threshold of $\tau = 8$ degrees
% TODO: how to motivate this threshold?
\begin{figure}[t]
	\centering
	\includegraphics[width=3.5in]{figures/tt_deadlen.pdf}
	\caption{\label{fig:tt_deadlen}Box plot of the amount of time the target is near the crosshairs versus the length of sensor dropouts.}
\end{figure}
Using this threshold we measure a participant's \emph{time to failure}, the time until the a lost state is encountered.  However, this may not be a very descriptive measure, since a participant may reach the lost state sooner or later depending on the movement of the avatars, which varies between trials.

We also consider a measurement we call \emph{time following target}, which is the amount of time spent successfully following the target.  This metric seems to most generally represent how well a participant performed.  Trials with either more or longer lost periods will result in a lower total time following the target.

For a more specific measure of performance, we count the number of times a participant reaches the lost state in a trial, or  \emph{number of times lost}.  We only record a lost state when the error stays above the threshold $\tau$ for a minimum of 4 seconds.  A 4 second threshold was used because it is double the maximum dropout length, allowing the user a few seconds to resume successful tracking after the dropout before they are considered to have lost the target.
% TODO: how to motivate this threshold?
